Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Added median runtime improvement to introduction.
Added median runtime improvement introduced by the abstraction to the
introduction.
completeness

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is $7.9$ seconds, and most controllers can be synthesized in less
than $17.2$ seconds.

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}
More details on how to model quantization as noise are given in the 
Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$

@@

The median runtime for our benchmark set is 7.9\,s.  Overall,
the average synthesis time amounts to approximately 17.2\,s.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.

>>>>

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is $7.9$ seconds, and most controllers can be synthesized in less
than $17.2$ seconds. We further show that, in a direct comparison, the abstraction-based
approach lowers the median runtime of our benchmarks by a factor of seven over the
multi-staged approach.

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
More details on how to model quantization as noise are given in the 
Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$

@@

The median runtime for our benchmark set is 7.9\,s.  Overall,
the average synthesis time amounts to approximately 17.2\,s.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  
There are several cases for which the system may fail to find a controller. In the naive approach,
there is the risk of the completeness threshold being too large, thus causing a timeout.
In the abstraction case, there is the risk of requiring a very precise abstraction, resulting in too many refinements which may timeout.
Other sources for incompleness are the inability of the {\sc synthesize} phase to use a large enough precision for the plant model in a given problem.
